% Created 2021-02-16 Tue 06:25
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{TEC}
\date{\today}
\title{Org knit}
\hypersetup{
 pdfauthor={TEC},
 pdftitle={Org knit},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

Let someone else take care of keeping up to date tangled/woven versions of your
Org files for public consumption.

\begin{verbatim}
- name: Export org files
  uses: tecosaur/org-knit-action
  with:
    github_token: ${{ secrets.GITHUB_TOKEN }}
\end{verbatim}

\section{Parameters}
\label{sec:org298163a}
\begin{description}
\item[{\texttt{parameter} (\texttt{default})}] description
\end{description}
\subsection{Exporting}
\label{sec:org2765774}
\begin{description}
\item[{\texttt{config} (\texttt{false})}] Path to either an \texttt{init.el} file, or a repository url for \texttt{\textasciitilde{}/.emacs.d}.
This also recognises Doom configuration repositories (\texttt{\textasciitilde{}/.config/doom}).
\item[{\texttt{setup\_file} (\texttt{false})}] URL for a \texttt{\#+setupfile} to use in all Org files.
\item[{\texttt{eval} (\texttt{false})}] Whether to evaluate code in Org files. Also accepts a list of
globs specifying which Org files should be evaluated.
\item[{\texttt{tangle} (\texttt{false})}] Whether to run \texttt{org-tangle} for each Org file. Also accepts a list of
globs specifying which Org files should be tangled.
\item[{\texttt{export} (\texttt{html})}] Comma separated list of formats to export to.
\item[{\texttt{files} (\texttt{**/*.org})}] List of org file globs to act on.
\end{description}
\subsection{Publishing}
\label{sec:orge7f1a35}
\begin{description}
\item[{\texttt{github\_token}}] The \texttt{GITHUB\_TOKEN} secret. Required to push any result.
\item[{\texttt{branch} (default branch)}] The branch to push files to
\item[{\texttt{force\_orphan} (\texttt{false})}] Force-push the created commit as the only commit on
the branch.
\item[{\texttt{keep\_files} (\texttt{true})}] Whether to include non-org-related files. Also accepts a
list of globs.
\item[{\texttt{commit\_message} (\texttt{Knit: !\#!})}] Commit message to use. \texttt{!\#!} is replaced with the
triggering commit hash.
\item[{\texttt{fragile} (\texttt{true})}] Fail the action if any export/tangle steps fail.
\end{description}
\end{document}
